MSDS6372Project1

### 2021-01-26 MSDS6372Project1.Rmd
clean up code restart objective 1

```{r}
library(tidyverse)
library(ggplot2)
library(GGally)
# You need to adjust the work environment to run this code
setwd("/Users/mingyang/Desktop/SMU/Applied Statistics/MSDS6372Project1")
# Directly import cleaned dataset and start from here
CarData = read.csv("CleanedCarData.csv")
# Convert factor variables
variables.to.factor = c("Make","Model","EngineFuelType","TransmissionType","DrivenWheels","MarketCategory","VehicleSize","VehicleStyle","Crossover","Diesel","Exotic","Luxury","HighPerformance","FactoryTuner","Performance","FlexFuel","Hatchback","Hybrid","N_A")
CarData[variables.to.factor] = lapply(CarData[variables.to.factor],factor)
summary(CarData)
# Plot agsint numeric variables
CarData %>% select(MSRP,Year,EngineHP,EngineCylinders,NumberOfDoors,HighwayMPG,CityMPG,Popularity) %>% ggpairs()
# Try Log transformation on MSRP
CarData$LogMSRP = log(CarData$MSRP)
# Recheck the logMSRP against numeric variables
# LogMSRP seem to have improved linear relationship between Year and EngineHP correlations
CarData %>% select(LogMSRP,Year,EngineHP,EngineCylinders,NumberOfDoors,HighwayMPG,CityMPG,Popularity) %>% ggpairs()
# Look at Popularity
boxplot(CarData$Popularity)
CarData %>% select(LogMSRP,Popularity)%>% ggpairs()
#Try LogPopularity
CarData$LogPopularity = log(CarData$Popularity)
CarData %>% select(LogMSRP,LogPopularity)%>% ggpairs()
# Look at original MSRP vs Popularity
CarData %>% select(MSRP,Popularity)%>% ggpairs()
#LogMSRP and LogPopularity seem to have improved the linearity relationship between the two
# Look at histogram of LogMSRP
CarData %>% ggplot(aes(x=LogMSRP))+geom_histogram(bins=100)
# Drop MSRP and Popularity from the original Dataset
CarData<-CarData[,-c(15,16)]
# Drop MarketCategory - 72 levels are not useful for prediction
CarData <-CarData[,-10]
str(CarData)
#Split data into 80% Train 10% Test 10% Validation set
set.seed(111)
train.test.index<-sample(1:dim(CarData)[1],10723,replace=F)
train.test = CarData[train.test.index,]
validate = CarData[-train.test.index,]
set.seed(112)
train.index = sample(1:dim(train.test)[1],9531,replace=F)
train = train.test[train.index,]
test = train.test[-train.index,]

# Use Forward variable selection method to select possible variables as predictors
library(leaps)
reg.fwd=regsubsets(LogMSRP~.,data=train,method="forward",nvmax=955)
par(mfrow=c(1,3))
bics<-summary(reg.fwd)$bic
plot(1:956,bics,type="l",ylab="BIC",xlab="# of predictors")
index<-which(bics==min(bics))
points(index,bics[index],col="red",pch=10)

adjr2<-summary(reg.fwd)$adjr2
plot(1:956,adjr2,type="l",ylab="Adjusted R-squared",xlab="# of predictors")
index<-which(adjr2==max(adjr2))
points(index,adjr2[index],col="red",pch=10)

rss<-summary(reg.fwd)$rss
plot(1:956,rss,type="l",ylab="train RSS",xlab="# of predictors")
index<-which(rss==min(rss))
points(index,rss[index],col="red",pch=10)

coef(reg.fwd,676)
# By using Forward method, 676 predictors seem to generate the smallest BIC number
# This model has selected predictors below:
# Make+Model+EngineFuelType+TransmissionType+VehicleSize+VehicleStyle+HighwayMPG+CityMPG+Luxury+FactoryTuner+Performance+FlexFuel+Hybrid+N_A+Exotic+Hatchback+LogPopularity
forward.regression = lm(LogMSRP~Make+Model+EngineFuelType+TransmissionType+VehicleSize+VehicleStyle+HighwayMPG+CityMPG+Luxury+FactoryTuner+Performance+FlexFuel+Hybrid+N_A+Exotic+Hatchback+LogPopularity,data=train)
summary(forward.regression)
par(mfrow=c(2,2))
plot(forward.regression)
library(olsrr)
ols_plot_cooksd_bar(forward.regression)
ols_plot_resid_stand(forward.regression)
# After observing the Cook's D, there is observation 4659, 9435 has extremely large Cook's D
# Observation 1523 also has large Cook's D
train[4659,] # Toyota Yaris iA
exp(train[4659,25]) 
train%>% filter(Make=="Toyota") %>% select(Make,Model,Year,LogMSRP)
# Can't really make sense to eliminate observation 4659

train[9435,] # Ferrari Superamerica 2005
exp(train[9435,25]) # Exotic Car

#Look at other Exotic Cars
train%>%filter(Exotic=="Yes")%>% select(Make,Model,Year,LogMSRP,LogPopularity)
# Don't really make sense to delete observation 4659 either

# Since there are so many categorical variables, and log transformation improvement on Year and EngineHP didn't make it to the final model
# Next section we will try reimport the dataset without transformation
```

#### Objective 1 continue without Log transformation - since there are so many categorical variables

```{r}
library(tidyverse)
library(ggplot2)
library(GGally)
# You need to adjust the work environment to run this code
setwd("/Users/mingyang/Desktop/SMU/Applied Statistics/MSDS6372Project1")
# Directly import cleaned dataset and start from here
CarData = read.csv("CleanedCarData.csv")
###################################################################################
# Restrict prediction range to over cars under 1 million... To improve precision###
###################################################################################
CarData = CarData %>% filter(MSRP < 1000000)
# Convert factor variables
variables.to.factor = c("Make","Model","EngineFuelType","TransmissionType","DrivenWheels","MarketCategory","VehicleSize","VehicleStyle","Crossover","Diesel","Exotic","Luxury","HighPerformance","FactoryTuner","Performance","FlexFuel","Hatchback","Hybrid","N_A")
CarData[variables.to.factor] = lapply(CarData[variables.to.factor],factor)
summary(CarData)
# Plot agsint numeric variables
# CarData %>% select(MSRP,Year,EngineHP,EngineCylinders,NumberOfDoors,HighwayMPG,CityMPG,Popularity) %>% ggpairs()
CarData = CarData[,-10] #delete MarketCategory
# Try different way of sampling by Models

@@

str(train)
str(CarData)
# Use Forward variable selection method to select possible variables as predictors
########################################
# Try Forward selection model.##########
########################################
library(leaps)
reg.fwd=regsubsets(MSRP~.,data=train,method="forward",nvmax=963)
par(mfrow=c(1,3))
bics<-summary(reg.fwd)$bic
plot(1:964,bics,type="l",ylab="BIC",xlab="# of predictors")
index<-which(bics==min(bics))
points(index,bics[index],col="red",pch=10)

>>>>

# Start Here... Load in cleanedData, delete over 1 million dollar cars
## split dataset into train/test/validate sets with set seed number
### Models that only have 5 observations will all end up in train set
```{r}
library(tidyverse)
library(ggplot2)
library(GGally)
# You need to adjust the work environment to run this code
setwd("/Users/mingyang/Desktop/SMU/Applied Statistics/MSDS6372Project1")
# Directly import cleaned dataset and start from here
CarData = read.csv("CleanedCarData.csv")
###################################################################################
# Restrict prediction range to over cars under 1 million... To improve precision###
###################################################################################
CarData = CarData %>% filter(MSRP < 1000000)
# Convert factor variables
variables.to.factor = c("Make","Model","EngineFuelType","TransmissionType","DrivenWheels","MarketCategory","VehicleSize","VehicleStyle","Crossover","Diesel","Exotic","Luxury","HighPerformance","FactoryTuner","Performance","FlexFuel","Hatchback","Hybrid","N_A")
CarData[variables.to.factor] = lapply(CarData[variables.to.factor],factor)
summary(CarData)
# Plot agsint numeric variables
# CarData %>% select(MSRP,Year,EngineHP,EngineCylinders,NumberOfDoors,HighwayMPG,CityMPG,Popularity) %>% ggpairs()
CarData = CarData[,-10] #delete MarketCategory
# Try different way of sampling by Models

@@

str(train)
str(CarData)
```

This model need to be highly interpretable. We need to provide interpretation of the regression coefficients of the final model including hypothesis testing, interpretation of regression coefficients, and confidence intervals.

```{r}

#### Objective 2 start without Log transformation - since there are so many categorical variables

```{r}
# Use Forward variable selection method to select possible variables as predictors
########################################
# Try Forward selection model.##########
########################################
library(leaps)
reg.fwd=regsubsets(MSRP~.,data=train,method="forward",nvmax=963)
par(mfrow=c(1,3))
bics<-summary(reg.fwd)$bic
plot(1:964,bics,type="l",ylab="BIC",xlab="# of predictors")
index<-which(bics==min(bics))
points(index,bics[index],col="red",pch=10)
